%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Kadir Jun}{Ayhan}

\position{Ph.D.}
\address{52 Ewhayeodae-gil, Daehyeon-dong, Seodaemun-gu, Seoul, Republic
of Korea}

\mobile{+82-2-3277-4628}
\email{\href{mailto:ayhan@ewha.ac.kr}{\nolinkurl{ayhan@ewha.ac.kr}}}
\homepage{kjayhan.github.io}
\github{kjayhan}
\linkedin{kadirjunayhan}
\twitter{kadirayhan}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{Assistant Professor of International Relations at Ewha Womans
University Graduate School of International Studies.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\thepage}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Ph.D. in International Studies}{Seoul National University Graduate School of International Studies}{Seoul, South Korea}{2016}{}\vspace{-4.0mm}
    \cventry{Master in International Studies}{Seoul National University Graduate School of International Studies}{Seoul, South Korea}{2010}{}\vspace{-4.0mm}
    \cventry{Bachelor of Commerce in Economics, International Trade (Double Majors)}{The University of Auckland}{Auckland, New Zealand}{2008}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{professional-experience-selected}{%
\section{Professional Experience
(Selected)}\label{professional-experience-selected}}

\begin{cventries}
    \cventry{Assistant Professor}{Graduate School of International Studies}{Ewha Womans University}{March 2021 - Present}{\begin{cvitems}
\item Ph.D. Director
\item Public Diplomacy Center Vice Director
\end{cvitems}}
    \cventry{Member}{Steering Advisory Committee for Empowerment of Cultural Exchanges and Cooperation}{Korea Foundation}{October 2021 - Present}{}\vspace{-4.0mm}
    \cventry{Member}{National Unity Committee}{Republic of Korea Presidential Transition Committee}{April 2022 - June 2022}{}\vspace{-4.0mm}
    \cventry{Visiting Professor}{Division of International Studies}{Hankuk University of Foreign Studies}{March 2020 - February 2021}{}\vspace{-4.0mm}
    \cventry{Assistant Professor}{Graduate School of International and Area Studies}{Hankuk University of Foreign Studies}{March 2017 - February 2020}{}\vspace{-4.0mm}
    \cventry{Visiting Fellow}{Institute for Public Diplomacy and Global Communication}{George Washington University}{June 2018 - August 2018}{}\vspace{-4.0mm}
    \cventry{Lecturer}{Graduate School of International Studies}{Seoul National University}{September 2015 - February 2017}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{journal-articles}{%
\subsection{Journal Articles}\label{journal-articles}}

\hypertarget{refs_journals}{}
\leavevmode\vadjust pre{\hypertarget{ref-ayhan_inter-korean_nodate}{}}%
\textbf{Ayhan, K.} J., \& Jang, S. (n.d.). Inter-{Korean}
{People}-to-{People} {Diplomacy}: {Social} and {Cultural} {Exchanges}
across the 38th {Parallel}. \emph{The Hague Journal of Diplomacy}.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_english_2022}{}}%
\textbf{Ayhan, K.} J. (2022). An {English} {School} of {International}
{Relations} {Approach} to {Public} {Diplomacy}: {A} {Public} {Diplomacy}
{Framework} for {Global} {Governance} {Issues}. \emph{Journal of Public
Diplomacy}, \emph{2}(1), 1--4.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_south_2022}{}}%
\textbf{Ayhan, K.} J. (2022). South {Korea}'s {Public} {Diplomacy}
during the {COVID}-19 {Pandemic}: {Seeking} {Status} as an {Authority}
in {Global} {Governance}. \emph{KEI Academic Paper Series}.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_exploring_2022}{}}%
\textbf{Ayhan, K.} J., Gouda, M., \& Lee, H. (2022). Exploring {Global}
{Korea} {Scholarship} as a {Public} {Diplomacy} {Tool}. \emph{Journal of
Asian and African Studies}, \emph{57}(4), 872--893.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_moving_2022}{}}%
\textbf{Ayhan, K.} J., \& Sevin, E. (2022). Moving public diplomacy
research forward: Methodological approaches. \emph{Place Branding and
Public Diplomacy}, \emph{18}(3), 201--203.

\leavevmode\vadjust pre{\hypertarget{ref-varpahovskis_impact_2022}{}}%
Varpahovskis, E., \& \textbf{Ayhan, K.} J. (2022). Impact of country
image on relationship maintenance: A case study of {Korean} {Government}
{Scholarship} {Program} alumni. \emph{Place Branding and Public
Diplomacy}, \emph{18}(2), 52--64.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_journal_2021}{}}%
\textbf{Ayhan, K.} J. (2021). Journal of {Public} {Diplomacy}: {Sunrise}
of a {New} {Interdisciplinary} {Journal} for an {Emerging} {Academic}
{Field}. \emph{Journal of Public Diplomacy}, \emph{1}(1), 1--4.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_determinants_2021}{}}%
\textbf{Ayhan, K.} J., \& Gouda, M. (2021). Determinants of {Global}
{Korea} {Scholarship} students' word-of-mouth about {Korea}. \emph{Asia
Pacific Education Review}, \emph{22}(1), 15--29.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_introduction_2021}{}}%
\textbf{Ayhan, K.} J., \& Snow, N. (2021). Introduction to the special
issue---{Global} {Korea} {Scholarship}: {Empirical} evaluation of a
non-{Western} scholarship program from a public diplomacy perspective.
\emph{Politics \& Policy}, \emph{49}(6), 1282--1291.

\leavevmode\vadjust pre{\hypertarget{ref-hong_international_2021}{}}%
Hong, M. S., Jeong, M., \& \textbf{Ayhan, K.} J. (2021). International
{Scholarship} for {Social} {Change}? {Re}-contextualizing {Global}
{Scholarship} {Alumni}'s {Perceptions} of {Diversity} and {Justice} in
{South} {Korea}. \emph{Politics \& Policy}, \emph{49}(6).

\leavevmode\vadjust pre{\hypertarget{ref-istad_global_2021}{}}%
Istad, F., Varpahovskis, E., Miezan, E., \& \textbf{Ayhan, K.} J.
(2021). Global {Korea} {Scholarship} students: {Intention} to stay in
the host country to work or study after graduation. \emph{Politics \&
Policy}, \emph{49}(6), 1323--1342.

\leavevmode\vadjust pre{\hypertarget{ref-jon_satisfied_2021}{}}%
Jon, J.-E., \& \textbf{Ayhan, K.} J. (2021). Satisfied or dissatisfied:
{The} determinants of {Global} {Korea} {Scholarship} recipients'
satisfaction with life in {Korea}. \emph{Politics \& Policy},
\emph{49}(6), 1391--1414.

\leavevmode\vadjust pre{\hypertarget{ref-sevin_capturing_2021}{}}%
Sevin, E., \textbf{Ayhan, K.} J., \& Ingenhoff, D. (2021). Capturing
country images: A methodological approach. \emph{The Journal of
International Communication}, \emph{27}(2), 237--257.

\leavevmode\vadjust pre{\hypertarget{ref-tam_evaluations_2021}{}}%
Tam, L., \& \textbf{Ayhan, K.} J. (2021). Evaluations of people,
affection, and recommendation for a host country: {A} study of {Global}
{Korea} {Scholarship} ({GKS}) recipients. \emph{Politics \& Policy},
\emph{49}(6), 1292--1307.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_exploration_2020}{}}%
\textbf{Ayhan, K.} J. (2020). An {Exploration} of {Korean} {Discourses}
on {Public} {Diplomacy}. \emph{Journal of Contemporary Eastern Asia},
\emph{19}(1), 31--42.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_transferring_2020}{}}%
\textbf{Ayhan, K.} J. (2020). Transferring {Knowledge} to {Narrative}
{Worlds}: {Applying} {Power} {Taxonomy} to {Science} {Fiction} {Films}.
\emph{International Studies Perspectives}, \emph{21}(3), 258--274.

\leavevmode\vadjust pre{\hypertarget{ref-sevin_analyzing_2020}{}}%
Sevin, E., \textbf{Ayhan, K.} J., \& Ingenhoff, D. (2020). Analyzing
{Country} {Images} through {Networks}: {Case} of {South} {Korea}.
\emph{Asian International Studies Review}, \emph{21}(2), 95--119.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_rethinking_2019}{}}%
\textbf{Ayhan, K.} J. (2019). Rethinking {Korea}'s {Middle} {Power}
{Diplomacy} as a {Nation} {Branding} {Project}. \emph{Korea Observer},
\emph{50}(1), 1--24.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_boundaries_2019}{}}%
\textbf{Ayhan, K.} J. (2019). The {Boundaries} of {Public} {Diplomacy}
and {Non}-{State} {Actors}: {A} {Taxonomy} of {Perspectives}.
\emph{International Studies Perspectives}, \emph{20}(1), 63--83.

\leavevmode\vadjust pre{\hypertarget{ref-choi_why_2019}{}}%
Choi, S., Tam, L., \textbf{Ayhan, K.} J., \& Lee, D. (2019). Why and
{How} {Do} {Sojourners} {Talk} about {Macao}? {Effects} of {Perceived}
{Risk} and {Expected} {Benefit}. \emph{Asian International Studies
Review}, \emph{20}(2), 29--51.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_branding_2018}{}}%
\textbf{Ayhan, K.} J. (2018). Branding {Korea} as {``{My} {Friend}'s
{Country}''}: {The} {Case} of {VANK}'s {Cyber} {Public} {Diplomats}.
\emph{Korea Observer}, \emph{49}(1), 51--81.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_special_2018}{}}%
\textbf{Ayhan, K.} J. (2018). Special {Issue} on {Soft} {Power} and
{Public} {Diplomacy} in {East} {Asia}. \emph{Journal of Contemporary
Eastern Asia}, \emph{17}(1), 1--4.

\leavevmode\vadjust pre{\hypertarget{ref-lee_why_2015}{}}%
Lee, G., \& \textbf{Ayhan, K.} J. (2015). Why {Do} {We} {Need}
{Non}-state {Actors} in {Public} {Diplomacy}?: {Theoretical}
{Discussion} of {Relational}, {Networked} and {Collaborative} {Public}
{Diplomacy}. \emph{Journal of International and Area Studies},
\emph{23}(1), 57--77.

\hypertarget{book-chapters}{%
\subsection{Book Chapters}\label{book-chapters}}

\hypertarget{refs_section}{}
\leavevmode\vadjust pre{\hypertarget{ref-ayhan_south_nodate}{}}%
\textbf{Ayhan, K.} J. (n.d.). South {Korean} {Public} {Diplomacy}
vis-à-vis the {United} {States}: {Finding} {Support} for {Policies} in
{Washington} {DC}. In M. Lerner (Ed.), \emph{Divided {America},
{Divided} {Korea}: {U}.{S}.-{Korean} {Relations} {During} and {After}
the {Trump} {Years}}. Cambridge University Press.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_ideas_2021}{}}%
\textbf{Ayhan, K.} J., \& Kim, Y. (2021). Ideas {Matter} in
{Inter}-{Korean} {Relations}: {Shifts} in {South} {Korea}'s {Foreign}
{Policy} {Interests} and {Behavior} {Vis}-à-{Vis} {North} {Korea}. In M.
Richey, J. P. Panda, \& D. A. Tizzard (Eds.), \emph{The {Future} of the
{Korean} {Peninsula} {Korea} 2032 and {Beyond}} (pp. 32--58). Routledge.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_non-coercive_2021}{}}%
\textbf{Ayhan, K.} J., \& Sevin, E. (2021). Non-{Coercive} {Influence}
in {World} {Politics}: {Intersection} with {State} {Inclusive} {Index}.
In J. Park \& H.-S. Lyu (Eds.), \emph{Developing {State} {Inclusiveness}
{Index}: {Conceptualization} and {Measurement}} (pp. 419--435). National
Research Council for Economics, Humanities; Social Sciences.

\leavevmode\vadjust pre{\hypertarget{ref-lee_news_2021}{}}%
Lee, H., Jang, S., \& \textbf{Ayhan, K.} J. (2021). News {Coverage}
about the {U}.{S}. In {Korea} during {Bush}, {Obama} and {Trump}
{Administration}: {Trump} as an {Outlier}. In Y. R. Kamalipour (Ed.),
\emph{Global {Media} {Perceptions} of the {United} {States}: {The}
{Trump} {Effect}} (pp. 175--188). Rowman \& Littlefield Publishing.

\leavevmode\vadjust pre{\hypertarget{ref-sevin_evaluation_2021}{}}%
Sevin, E., \& \textbf{Ayhan, K.} J. (2021). Evaluation in {Public}
{Diplomacy}. In D. Spry (Ed.), \emph{Communicating with {Purpose} and
{Value}: {ASEF} {Public} {Diplomacy} {Handbook}} (pp. 61--68).
Asia-Europe Foundation (ASEF).

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_mingan_2020}{}}%
\textbf{Ayhan, K.} J. (2020). Mingan {Bunyaeui} {Gonggong} {Waegyo}
{[}{People}-to-{People} {Diplomacy}{]}. In K. Foundation (Ed.),
\emph{Cheoeum {Mannaneun} {Gonggong} {Waegyo}}. Korea Foundation.

\leavevmode\vadjust pre{\hypertarget{ref-sevin_assessing_2019}{}}%
Sevin, E., \textbf{Ayhan, K.} J., Jang, W. Y., \& Lee, H. (2019).
Assessing {Propaganda} {Effectiveness} in {North} {Korea}: {A} {Limited}
{Access} {Case} {Study}. In P. Baines, N. J. O'Shaughnessy, \& N. Snow
(Eds.), \emph{Handbook of {Propaganda}} (pp. 205--222). Sage.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_koreas_2017}{}}%
\textbf{Ayhan, K.} J. (2017). Korea's {Soft} {Power} and {Public}
{Diplomacy} {Under} {Moon} {Jae}-{In} {Administration}: {A} {Window}
{Of} {Opportunity}. In K. J. Ayhan (Ed.), \emph{Korea's {Soft} {Power}
and {Public} {Diplomacy}} (pp. 13--32). Hangang Network.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_introduction_2016}{}}%
\textbf{Ayhan, K.} J. (2016). Introduction. In K. J. Ayhan (Ed.),
\emph{Korea's {Public} {Diplomacy}}. Hangang Network.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_utilizing_2014}{}}%
\textbf{Ayhan, K.} J. (2014). Utilizing {Non}-state {Actors} for
{Korean} {Public} {Diplomacy}. In B. M. Howe (Ed.), \emph{Korea in the
{World}: {Promoting} {Mutual} {Understanding} and {Global}
{Partnerships}} (pp. 127--170). Ministry of Foreign Affairs \& Ewhan.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_analysis_2013}{}}%
\textbf{Ayhan, K.} J. (2013). An {Analysis} of the {Nexus} between
{Popular} {Culture} {Consumption} and {East} {Asian} {Regionalisation}
{Space} and {Place}. In D. Kılıçkıran, C. Alegria, \& C. Haddrell
(Eds.), \emph{Space and {Place}: {Exploring} {Critical} {Issues}} (pp.
165--174). Brill.

\hypertarget{books}{%
\subsection{Books}\label{books}}

\hypertarget{refs_books}{}
\leavevmode\vadjust pre{\hypertarget{ref-ayhan_koreas_2017}{}}%
\textbf{Ayhan, K.} J. (2017). \emph{Korea's {Soft} {Power} and {Public}
{Diplomacy}}. Hangang Network.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_koreas_2016}{}}%
\textbf{Ayhan, K.} J. (2016). \emph{Korea's {Public} {Diplomacy}}.
Hangang Network.

\hypertarget{book-reviews}{%
\subsection{Book Reviews}\label{book-reviews}}

\hypertarget{refs_reviews}{}
\leavevmode\vadjust pre{\hypertarget{ref-ayhan_competition_2020}{}}%
\textbf{Ayhan, K.} J. (2020). Competition for {Hearts} and {Minds}:
{Cold} {War} {Public} {Diplomacy}. \emph{International Studies Review},
\emph{22}(4), 988--989. \url{https://doi.org/10.1093/isr/viaa038}

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_book_2019}{}}%
\textbf{Ayhan, K.} J. (2019). {[}{Book} {Review} for {James} {Pamment}
and {Karin} {Gwinn} {Wilkins} ({Eds}.) (2018). {Communicating}
{National} {Image} through {Development} and {Diplomacy}: {The}
{Politics} of {Foreign} {Aid}. {Palgrave} {Macmillan}{]}.
\emph{International Journal of Communication}, \emph{13}, 1--4.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_book_2019-1}{}}%
\textbf{Ayhan, K.} J. (2019). {[}{Book} {Review} for {Scott} {A}.
{Snyder} (2018). {South} {Korea} at the {Crossroads}: {Autonomy} and
{Alliance} in an {Era} of {Rival} {Powers}. {Columbia} {University}
{Press}{]}. \emph{International Affairs}, \emph{95}(4), 961--962.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_book_2018}{}}%
\textbf{Ayhan, K.} J. (2018). {[}{Book} {Review} for {Review} of the
book {[}{Wiseman}, {G}. (2015). {Isolate} or {Engage}: {Adversarial}
{States}, {U}.{S}. {Foreign} {Policy}, and {Public} {Diplomacy}.
{Stanford} {University} {Press}{]}. \emph{Croatian International
Relations Review}, \emph{24}(81), 146--149.

\leavevmode\vadjust pre{\hypertarget{ref-ayhan_connecting_2018}{}}%
\textbf{Ayhan, K.} J. (2018). Connecting {Public} {Diplomacy} and
{Foreign} {Policy}. \emph{International Studies Review}, \emph{20}(3),
539--540.

\hypertarget{grants}{%
\section{Grants}\label{grants}}

\begin{cventries}
    \cventry{Korea International Economic Policy}{Graduate Program for Area Studies (European Studies)}{Ewha Womans University Graduate School of International Studies}{2022-23}{\begin{cvitems}
\item 100 million KRW (roughly \$75,000)
\end{cvitems}}
    \cventry{Korea Foundation}{Korean-German Junior Forum}{Ewha Public Diplomacy Center (with Kisuk Cho)}{2022}{\begin{cvitems}
\item 61.72 million KRW (roughly \$47,000)
\end{cvitems}}
    \cventry{Ewha Womans University}{Incentive Award Research Project: “Rethinking Soft Power from Power-recipient’s Perspective”}{Individual}{2022}{\begin{cvitems}
\item 3.6 million KRW (roughly \$3,000)
\end{cvitems}}
    \cventry{Korea Foundation}{Korean-German Junior Forum}{Ewha Public Diplomacy Center (with Kisuk Cho)}{2021}{\begin{cvitems}
\item 34 million KRW (roughly \$30,000)
\end{cvitems}}
    \cventry{Ewha Womans University}{New Faculty Research Project: “International Student Mobility Programs in International Relations Theory”}{Individual}{2021}{\begin{cvitems}
\item 20 million KRW (roughly \$18,000)
\end{cvitems}}
    \cventry{Korean Ministry of Foreign Affairs}{“Korea’s Public Diplomacy Article Contest” and book on the same topic}{Global Public Diplomacy Center}{2020}{\begin{cvitems}
\item 18.7 million KRW (roughly \$15,000)
\end{cvitems}}
    \cventry{Korea Foundation}{Policy-oriented Research Support Program: “An Experiment on the Effects of Social Identification on Support for Inter-Korean Public Diplomacy Policies Using Mediated and Interpersonal Communication”}{with Lindsey Bier, Park Han-Woo and Park Sejung}{2020}{\begin{cvitems}
\item \$50,000
\end{cvitems}}
    \cventry{NSF-funded (SSEER) network, CONVERGE facility, Natural Hazards Center at University of Colorado Boulder}{CONVERGE facility, Natural Hazards Center at University of Colorado Boulder: “Mapping China’s Public Diplomacy Operations on Twitter, during the COVID-19 Crisis,” COVID-19 Working Group for Public Health and Social Sciences Research}{with Weiai Xu, Rui Wang, Celine Song and Miao Feng}{2020}{\begin{cvitems}
\item \$1000
\end{cvitems}}
    \cventry{Korea Foundation,  () (30 million KRW, roughly \$27,000)}{Policy-oriented Research Support Program: “Empowerment of Public Diplomacy Curriculum at Universities”}{Hankuk University of Foreign Studies (with Lee Sang-Hwan et al.)}{2019}{\begin{cvitems}
\item 30 million KRW (roughly \$27,000)
\end{cvitems}}
    \cventry{Academy of Korean Studies}{Korean Studies Grant: “Capturing the Imagined Reality: A Study of South Korean Country Image”}{with Efe Sevin and Diana Ingenhoff}{2019}{\begin{cvitems}
\item \$40,000
\end{cvitems}}
    \cventry{Korea Foundation}{Policy-oriented Research Support Program: “Rethinking Inter-Korean Social Exchanges in Turbulent Times”}{with Rafal Smoczynski and Park Han-Woo}{2019}{\begin{cvitems}
\item \$50,000
\end{cvitems}}
    \cventry{Korea Foundation}{Policy-oriented Research Support Program: Realizing the Public Diplomacy Potential of Korean Government Scholarship- A Mixed Study of Alumni and Current Students”}{with Nancy Snow and Moamen Gouda}{2019}{\begin{cvitems}
\item \$40,000
\end{cvitems}}
    \cventry{Korea Foundation}{Policy-oriented Research Support Program: “People-to-People Diplomacy in Inter-Korean Relations”}{with Rafal Smoczynski}{2018}{\begin{cvitems}
\item \$50,000
\end{cvitems}}
    \cventry{Korea Foundation}{Policy-oriented Research Support Program: “Korean Government Scholarship Program (KGSP) as a Public Diplomacy Tool”}{with Nancy Snow}{2018}{\begin{cvitems}
\item \$40,000
\end{cvitems}}
    \cventry{Korean Ministry of Foreign Affairs}{“Korea’s Diplomacy and Soft Power Conference”, article contest, and book on same topic}{Hangang Network}{2017}{\begin{cvitems}
\item 19.8 million KRW (roughly \$18,000)
\end{cvitems}}
    \cventry{Korean Ministry of Foreign Affairs}{“Seoul Youth Forum” (16 events) on Korea’s Nation-Branding Strategy}{Hangang Network}{2016}{\begin{cvitems}
\item 20 million KRW (roughly \$18,000)
\end{cvitems}}
    \cventry{Korean Ministry of Foreign Affairs}{“Korea’s Public Diplomacy Conference”, article contest, and book on same topic}{Hangang Network}{2016}{\begin{cvitems}
\item 20 million KRW (roughly \$18,000)
\end{cvitems}}
\end{cventries}

\hypertarget{invited-talks-selected}{%
\section{Invited Talks (Selected)}\label{invited-talks-selected}}

\begin{cventries}
    \cventry{Jeju Forum - Korea Foundation Session}{Universal Values-based Public Diplomacy: Towards Peaceful Coexistence}{Jeju}{2022, September 14}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea-China 30th Anniversary of Diplomatic Relations Expert and Youth Forum}{30 Years of Korea-China Diplomatic Relations: Omnidirectional Diplomacy and Public Diplomacy}{Global Strategic Cooperation Research Center, Seoul}{2022, August 23}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{2022 Daegu-Gyeongbuk Public Diplomacy Symposium}{The Development Process of Public Diplomacy and Various Cases across the World}{Daegu}{2022,  June 3}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{72nd International Communication Association Annual Conference}{BLUE SKY WORKSHOP: Connecting Global South and Global North: Toward Decolonization of Public Diplomacy Scholarship and Methodology}{Zoom}{2022, May 27}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{2022 Overseas Koreans Friends Homecoming/ Cyber Youth Camp}{Public Diplomacy Cases from Across the World}{Studio recording}{2022, May 18}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Asia Europe Foundation’s 9th Public Diplomacy Training: Communicating with Purpose and Value}{Evaluation}{Zoom}{2022, April 13}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea Economic Institute}{South Korea’s Public Diplomacy during the COVID-19 Pandemic and Beyond}{Washington D.C.}{2022, January 27}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea-US Public Diplomacy Forum}{Panel: The Role of Korea-U.S. Public Diplomacy to Strengthen Alliance}{HUFS Media Diplomacy Center, Seoul}{2021, October 5}{}\vspace{-4.0mm}
    \cventry{Panel: From Korea with Luv: South Korean Public Diplomacy in the Third Korean Wave}{Korea’s Public Diplomacy: Objectives, Actors, and Activities}{The University of Philippines Korea Research Center (Zoom)}{2021, August 6}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Citizen Diplomacy Research Group}{People-to-people Diplomacy: Empowerment of Citizens by Korea Foundation}{The University of Philippines Korea Research Center (Zoom)}{2021, August 4}{}\vspace{-4.0mm}
    \cventry{Public Diplomacy Camp}{Public Diplomacy: Yesterday,  Today and Tomorrow}{Korea Foundation}{2021, July 31}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Public Diplomacy in Asia 2021}{Panel: Different Approaches in Measuring and Evaluating the Effectiveness of Public Diplomacy}{Korea Foundation}{2021, July 27}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Training for Korea Foundation Staff}{Public Diplomacy Complemented and Supplemented by Civil Society: The Case of Korea}{Korea Foundation}{2021, July 22}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{InAsia Forum}{South Korea’s Global Status-Seeking in a Multiplex World Order}{The Institute for Far Eastern Studies}{2021, June 6}{}\vspace{-4.0mm}
    \cventry{Gwangju Democracy Forum}{Democracy and Korea’s Public Diplomacy: Beyond Rhetoric}{Zoom}{2021, May 20}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{University of Southern California}{Korea’s Public Diplomacy: Objectives, Actors and Activities}{Zoom}{2021, April 21}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{The KAPD 2020 International Conference \& Annual Conference: Public Diplomacy in the Age of Great Transformation}{Status-Seeking in a Multiplex World Order: Korea’s Public Diplomacy in the Age of COVID-19}{Seoul}{2020 November 27}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Keimyung University}{Public Diplomacy Cases from around the World}{Zoom}{2020, November 17}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{C20 Korea Forum}{G20 and Korea’s Public Diplomacy}{KOICA}{2020, November 12}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{The 6th International Symposium of Asian Development Studies}{Active Learning in Digitalized Education: Challenges and Opportunities}{Zoom}{2020, October 23}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea Foundation}{Host for 3rd Public Diplomacy Week of Korea Foundation Keynote Session with Joseph Nye}{Live Studio Recording}{2020, October 14}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea Global Forum for Peace 2020}{Inter-Korean People-to-People Diplomacy: Social and Cultural Exchanges across the 38th Parallel}{Zoom}{2020, September 8}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea Foundation (Orientation for People-to-People Diplomacy Project Participants)}{Relational People-to-People Diplomacy}{Zoom}{2020, June 27}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Korea Foundation}{Public Diplomacy Cases from around the World}{Youtube recording in studio}{2020, June 15}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Korea Foundation (Public Diplomacy Practitioner Training)}{Korean Public Diplomacy in the 2020s}{Zoom}{2020, June 11}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Jeju University-Korea Foundation Conference on COVID-19 and Public Diplomacy}{Turkish Public Diplomacy amid COVID-19: Status-Seeking in a Multiplex World Order}{Zoom}{2020, June 3}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Chungnam University}{People-to-People Diplomacy}{Recorded Lecture}{2020, June 1}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Sookmyung Women’s University}{Social Identity and Intergroup Communication}{Zoom}{2020, April 7}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Ajou University}{Understanding Power in World Politics}{Suwon}{2019, December 9}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Jeju National University}{History and Future of Public Diplomacy}{Jeju}{2019, November 28}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Ajou University}{Climate Action Simulation}{Suwon}{2019, November 25}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Keimyung University}{Foreign Policy Objectives and Public Diplomacy in 2010s}{Daegu}{2019, November 11}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Ministry of Foreign Affairs Policy-oriented Public Diplomacy Advisory Meeting}{Assessment and Evaluation in Korean Public Diplomacy}{Incheon}{2019, November 9}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Chungnam University}{History and Present of Public Diplomacy}{Daejon}{2019, November 4}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Korea Foundation}{Understanding People-to-People Diplomacy}{Seoul}{2019, August 19}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Ministry of Foreign Affairs (closed roundtable)}{Let the Sun Shine? Inter-Korean People-to-People Diplomacy in the Absence of State-based Public Diplomacy}{Seoul}{2019, August 12}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea Foundation Public Diplomacy Academy}{Recent Trends in Public Diplomacy Literature}{Seoul}{2019, July 30}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Yonsei University}{Korean Public Diplomacy: Objectives, Actors, and Acvitivies}{Incheon}{2019, May 9}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Korea Public Diplomacy Association}{Relational Public Diplomacy at Grassroots}{Seoul}{2019, April 6}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{1st Public Diplomacy Week}{People-to-People Diplomacy in Korea}{Seoul}{2018, November 3}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{University of Warsaw}{How Do European Recipients of Korean Government Scholarship View Korea?}{Warsaw}{2018, October 5}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Jeju Forum - Ministry of Foreign Affairs Session}{Vision and Strategy of Public Diplomacy for Peace and Prosperity in the Korean Peninsula and in Northeast Asia}{Jeju}{2018, June 26}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{UNITAR CIFAL Jeju/ JITC Partnership Program for Diplomats}{Understanding Public Diplomacy}{Jeju}{2017, November 23}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Ministry of Foreign Affairs Roundtable Panel Discussion: Cultural Diplomacy with New Media at the era of the 4th Industrial Revolution}{Relational and Collaborative Dynamics of Cultural Diplomacy}{Seoul}{2017, November 21}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Ajou University CEO Education Program}{Cultural Diversity and Dialogue}{Suwon}{2017, October 24}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{UNITAR CIFAL Jeju/ JITC Policy Workshop: Cultural Tourism for Sustainable Development in the Asia-Pacific Region}{Sustainable Cultural Tourism for Economic Development}{Jeju}{2017, October 10}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Multicultural Education Academic Forum}{If We Guarantee Cultural Diversity, We Guarantee Korean Society’s Future}{Ministry of Education \& National Institute for Lifelong Education}{2016, November 10}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{UNESCO Korea Commission}{Cultural Diversity and Global Citizen” Global Citizenship Education}{Seoul}{2016, October 25}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Public Diplomacy and Returnees Forum}{Alumni as a Tool of Public Diplomacy}{Ministry of Foreign Affairs \& ISF}{2015, November 17}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{ISR Academy - International Sports Relations Foundation}{Relational Public Diplomacy through Sports}{Incheon}{2015, November 4}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{Policy Panel Forum: Introduction of Overseas Koreans’ Proportional Representation in the Parliament}{The Consequences of Turkish Election Campaigns in Europe}{Korean National Assembly, Seoul}{2015, April 27}{\begin{cvitems}
\item Korean
\end{cvitems}}
    \cventry{Working Group Developing Public Diplomacy Policy for Korea as Middle Power}{Sixth KF Global Seminar Middle Powers and Public Diplomacy Building a Network for the Global Public Good}{Korea Foundation, Seoul}{2013, November 21}{\begin{cvitems}
\item English
\end{cvitems}}
    \cventry{International Symposium for the Glocalization of Hallyu and Religion}{Hallyu in the Middle-East: Does Cultural Proximity or a Sense of Coevalness Exist?}{Yonsei University, Seoul}{2013, November 14}{\begin{cvitems}
\item English
\end{cvitems}}
\end{cventries}

\hypertarget{conference-presentations-selected}{%
\section{Conference Presentations
(Selected)}\label{conference-presentations-selected}}

\begin{cventries}
    \cventry{The Korean Association of International Studies Annual Conference}{The Determinants of US Public Diplomacy: Countering Adversary Influence All the Way}{Seoul}{2022 June}{}\vspace{-4.0mm}
    \cventry{International Studies Association Annual Convention}{The Determinants of United States’ Public Diplomacy Spending Abroad}{Zoom}{2022 March}{}\vspace{-4.0mm}
    \cventry{Korea-China 30th Anniversary of Diplomatic Relations Expert and Youth Forum}{An experiment on the multiplier effect: A study on inter-Korean people-to-people exchanges}{Zoom}{2022 March}{\begin{cvitems}
\item Ayhan, K. J., Park, S., Bier, L., Park, H.
\end{cvitems}}
    \cventry{Korean International Studies Association 13th Annual Convention \& Asia Pacific International Studies Association 15th Congress}{Does Democratization Work? United States’ Civil-society Aid and Democracy in the Recipient Countries}{Zoom}{2021 November}{\begin{cvitems}
\item Higgins, P., Ayhan, K. J.
\end{cvitems}}
    \cventry{International Communication Association Annual Conference}{Rethinking Soft Power with Alternative Explanations: Appealing to Fear, Appetite or Spirit}{Zoom}{2021 May}{}\vspace{-4.0mm}
    \cventry{International Communication Association Annual Conference}{Evaluations of People, Affective Connection and Recommendation toward a Host Country: Case Study of Global Korea Scholarship (GKS) Recipients}{Zoom}{2021 May}{\begin{cvitems}
\item Tam, L., Ayhan, K. J.
\end{cvitems}}
    \cventry{International Studies Association Annual Convention}{South Korea’s Global Status-Seeking in a Multiplex World Order}{Zoom}{2021 April}{}\vspace{-4.0mm}
    \cventry{International Studies Association Annual Convention}{The Process Evaluation of Korean Public Diplomacy: A Logic of Practice Approach}{Zoom}{2021 April}{\begin{cvitems}
\item Kim, Y., Ayhan, K. J.
\end{cvitems}}
    \cventry{The KAPD 2020 International Conference \& Annual Conference: Public Diplomacy in the Age of Great Transformation}{International Scholarship Students in South Korea: Determinants of Intention to Work in the Host Country After Graduation}{Zoom}{2020 November}{\begin{cvitems}
\item Istad, F., Varpahovskis, E., Miezan, E., Ayhan, K. J.
\end{cvitems}}
    \cventry{International Studies Association Asia-Pacific Conference}{Learning International Relations Theories in the Marvel Universe: The Black Panther of Wakanda}{Singapore}{2019 July}{\begin{cvitems}
\item Ayhan, K. J., Gouda, M.
\end{cvitems}}
    \cventry{KAIDEC Conference: In Search for a Sustainable Ecosystem for International Development: Challenges for the Future}{Development Dynamics of Korean Government Scholarship Program}{Seoul}{2019 June}{}\vspace{-4.0mm}
    \cventry{International Communication Association Pre-Conference: North Korea and Communication}{Let the Sun Shine? Inter-Korean People-to-People Diplomacy in the Absence of State-based Public Diplomacy}{Washington D.C.}{2019 May}{\begin{cvitems}
\item Ayhan, K. J., Jang, S.
\end{cvitems}}
    \cventry{WATEF Conference: Social Exchanges and Public Diplomacy on the Korean Peninsula}{Can the Country Image Predict Relationship Management Behavior}{Seoul}{2019 April}{\begin{cvitems}
\item Varpahovskis, E., Ayhan, K. J.
\end{cvitems}}
    \cventry{International Studies Association Annual Convention}{Nurturing Friends of Korea: Korean Government Scholarship Program as a Public Diplomacy Tool}{Toronto}{2019 March}{\begin{cvitems}
\item Ayhan, K. J., Gouda, M.
\end{cvitems}}
    \cventry{International Studies Association Annual Convention}{Roundtable: International Politics and Innovative Learning: (IPIL) - From Process to Progress}{Toronto}{2019 March}{}\vspace{-4.0mm}
    \cventry{International Studies Association Annual Convention}{Roundtable: New Perspectives on Non-State Diplomacy: Situating Empirical Framework in the Context of Non-Western Countries}{Toronto}{2019 March}{}\vspace{-4.0mm}
    \cventry{International Studies Association Midwest}{The Use of Science Fiction Films to Facilitate Active Cognitive Processing: The Power Workshop}{St. Louis}{2018 November}{}\vspace{-4.0mm}
    \cventry{International Studies Association Midwest}{How Do Korean Government Scholarship Recipients Think About Korea?}{St. Louis}{2018 November}{\begin{cvitems}
\item Ayhan, K. J., Gouda, M., Lee, H.
\end{cvitems}}
    \cventry{International Political Science Association 25th World Congress}{Ideas Matter in Inter-Korean Relations: Analyzing People-to-People Exchanges}{Brisbane}{2018 July}{}\vspace{-4.0mm}
    \cventry{International Studies Association Annual Convention}{Consolidating Global Korea Scholarship as a Public Diplomacy Tool}{San Francisco}{2018 April}{\begin{cvitems}
\item Ayhan, K. J., Gouda, M.
\end{cvitems}}
    \cventry{International Studies Association Annual Convention}{Korea’s Middle Power Diplomacy as a Nation Branding Project}{San Francisco}{2018 April}{}\vspace{-4.0mm}
    \cventry{Change in the Higher Education Landscape: The Power of Intercultural Networks in Innovative Learning (ISA Working Group)}{Active Learning through Critical Thinking: Identifying Power in Fictional Films}{San Francisco}{2018 April}{}\vspace{-4.0mm}
    \cventry{Korea International Studies Association Annual Conference}{Are We All Public Diplomats? A Classification of Korean ‘Diplomatic NGOs}{Seoul}{2017 November}{}\vspace{-4.0mm}
    \cventry{International Communication Association Annual Conference}{The Boundaries of Public Diplomacy Actorness: A Classification of Korean Diplomatic NGOs}{San Diego}{2017 May}{}\vspace{-4.0mm}
    \cventry{International Communication Association Post-Conference: Bridging Practice and Disciplinary Perspectives on the Formation and Effects of Country Image, Reputation, Brand, and Identity}{A Network of Young Korean Public Diplomacy Activists: VANK}{San Diego}{2017 May}{}\vspace{-4.0mm}
    \cventry{Korea in the World}{Utilizing Non-State Actors for South Korea’s Public Diplomacy}{Ewha Womans University, Seoul}{2014 May}{}\vspace{-4.0mm}
    \cventry{Change of Korean Society and Social Science’s Response}{Asking Social Connections and Volunteerism in Standardized Questions: The Case of Turkish Civil Society}{Seoul National University, Seoul}{2013 December}{}\vspace{-4.0mm}
    \cventry{ICAPA Annual Conference}{Popular Culture and East Asian Regionalization}{Ulaan Baatar}{2012 August}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{awards-and-honors}{%
\section{Awards and Honors}\label{awards-and-honors}}

\begin{cventries}
    \cventry{Korean Government Scholarship}{Korean Language Education and Ph.D. Program}{}{2010 - 2015}{}\vspace{-4.0mm}
    \cventry{Distinguished Thesis Award}{Seoul National University Graduate School of International Studies}{}{2010}{}\vspace{-4.0mm}
    \cventry{High Honor Award}{Seoul National University Graduate School of International Studies}{}{2010}{}\vspace{-4.0mm}
    \cventry{Scholarship}{Global Sharing Foundation}{}{2009}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\begin{cventries}
    \cventry{Instructor}{Graduate School of International Studies, Ewha Womans University}{}{2021 - Present}{\begin{cvitems}
\item Writing and Publishing a Journal Article
\item Soft Power in World Politics
\item International Security
\item International Relations of East Asia
\end{cvitems}}
    \cventry{Instructor}{Ewha Womans University}{}{2021 - Present}{\begin{cvitems}
\item Introduction to International Politics (Division of International Studies)
\item Public Diplomacy (International Summer College)
\end{cvitems}}
    \cventry{Instructor}{Center for Teaching and Learning, Hankuk University of Foreign Studies}{}{2020}{\begin{cvitems}
\item Digital Active Learning Pedagogy
\end{cvitems}}
    \cventry{Instructor}{Division of International Studies, Hankuk University of Foreign Studies}{}{2017 - 2021}{\begin{cvitems}
\item International Relations Theory
\item Public Diplomacy
\item Power in World Politics
\item International Relations of Asia
\item Transnational Actors in World Politics
\item Global Governance and NGOs
\end{cvitems}}
    \cventry{Instructor}{Graduate School of International and Area Studies, Hankuk University of Foreign Studies}{}{2017-2020}{\begin{cvitems}
\item Theory and Practice of Public Diplomacy
\item Soft Power and International Development Cooperation
\item Global Governance and NGOs
\item Transnational Issues and Actors in World Politics
\item Policy Analysis Workshop
\item Professional Development Seminar
\end{cvitems}}
    \cventry{Instructor}{Graduate School of International Studies, Seoul National University}{}{2015-2017}{\begin{cvitems}
\item Theory and Practice of Public Diplomacy
\item Global Governance and NGOs
\end{cvitems}}
    \cventry{Instructor}{Graduate School of International Studies, Ajou University}{}{2016-2017}{\begin{cvitems}
\item Global Governance and NGOs
\end{cvitems}}
\end{cventries}

\hypertarget{service-to-profession}{%
\section{Service to Profession}\label{service-to-profession}}

\begin{cventries}
    \cventry{Editor-in-Chief (Inaugural)}{Journal of Public Diplomacy}{}{2020 - Present}{}\vspace{-4.0mm}
    \cventry{Associate Editor}{Journal of Contemporary Eastern Asia}{}{2017 - Present}{}\vspace{-4.0mm}
    \cventry{Board Member (Inaugural)}{Korea Association for Public Diplomacy}{}{2020 - Present}{}\vspace{-4.0mm}
    \cventry{Executive Committee Member}{International Studies Association International Communication Section (ISA ICOMM)}{}{2020 - Present}{}\vspace{-4.0mm}
    \cventry{Section Chair}{International Studies Association International Communication Section (ISA ICOMM)}{}{2022 - Present}{}\vspace{-4.0mm}
    \cventry{Editor}{Korean Journal of International Studies}{}{2022 - Present}{}\vspace{-4.0mm}
    \cventry{Associate Editor}{Quality \& Quantity}{}{2019-2021}{}\vspace{-4.0mm}
    \cventry{Founder and Organizer}{Korea Public Diplomacy Colloquium (which later became the foundation of Korea Association for Public Diplomacy)}{}{2019 - 2020}{}\vspace{-4.0mm}
    \cventry{Outreach Committee Member}{Korea Association of International Development and Cooperation}{}{2018-2020}{}\vspace{-4.0mm}
    \cventry{Founding Member and Outreach Committee Member}{International Studies Association International Politics and Innovative Learning (IPIL) Network}{}{2018-2020}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{service-to-community}{%
\section{Service to Community}\label{service-to-community}}

\begin{cventries}
    \cventry{President}{Hangang Network for Academic and Cultural Exchanges}{}{2020 - Present}{\begin{cvitems}
\item 2016-2020, Executive Director
\end{cvitems}}
    \cventry{Vice Director}{New Silk Road Institute}{}{2018 - Present}{}\vspace{-4.0mm}
    \cventry{Co-founder and Board Member}{Global Public Diplomacy Center}{}{2019 - 2021}{}\vspace{-4.0mm}
    \cventry{Member}{Dol Dahm Club, Korea Ministry of Foreign Affairs}{}{2017 - 2019}{}\vspace{-4.0mm}
    \cventry{Honorary Envoy}{Korea's Public Diplomacy Scholars Group, Korea Ministry of Foreign Affairs}{}{2013 - 2017}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{advisor-reviewer-referee-jury-selected}{%
\section{Advisor/ Reviewer/ Referee/ Jury
(Selected)}\label{advisor-reviewer-referee-jury-selected}}

Korea Foundation, Korean Ministry of Foreign Affairs, International
Communication Association Public Diplomacy Interest Group,
\emph{International Studies Quarterly}, \emph{International Studies
Review}, \emph{International Studies Perspectives}, \emph{Politics},
\emph{Pacific Focus}, \emph{Korea Observer}, \emph{International Journal
of Communication}, \emph{International Journal of Cultural Policy},
\emph{International Journal of Communication}, \emph{Information
Processing and Management}, \emph{Globalizations}, \emph{Quality \&
Quantity}, \emph{Global Media and Communication}, \emph{The Hague
Journal of Diplomacy}, \emph{Place Branding and Public Diplomacy},
\emph{Journal of Marketing Communications}, \emph{Journal of
Contemporary Eastern Asia}, \emph{Insight Turkey}, \emph{Korean Journal
of International Studies}, \emph{Journal of International and Area
Studies}, \emph{Asian International Studies Review}, \emph{Pakistan
Journal of Social Sciences}

\hypertarget{certificates}{%
\section{Certificates}\label{certificates}}

\begin{cventries}
    \cventry{Participation}{Summer Institute for Computational Social Science – Korea (KAIST)}{}{2022}{}\vspace{-4.0mm}
    \cventry{Bayesian Modeling with RJAGS, Bayesian Regression Modeling with rstanarm, Fundamentals of Bayesian Data Analysis in R, Text Mining with Bag-of-Words in R, Introduction to Text Analysis in R, Datacamp Topic Modeling in R, Introduction to Python}{Datacamp}{}{2022}{}\vspace{-4.0mm}
    \cventry{Introduction to R, Intermediate R, Introduction to Tidyverse, Data Manipulation with dplyr, Joining Data with dplyr, Introduction to Data Visualization with ggplot2, Exploratory Data Analysis in R, Case Study: Exploratory Data Analysis in R, Introduction to Statistics in R, Intermediate Data Visualization, Reporting with RMarkdown, Introduction to Regression in R, Intermediate Regression in R}{Datacamp Data Scientist with R Track}{}{2021-2022}{}\vspace{-4.0mm}
    \cventry{R Basics, R Visualization, Probability, Inference and Modeling, Productivity Tools, Wrangling, Linear Regression, Machine Learning}{HarvardX on Edx Data Science Professional Certificate}{}{2021}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{other-publications}{%
\section{Other Publications}\label{other-publications}}

\textbf{Academic Blog Posts}

2020,
\href{https://www.uscpublicdiplomacy.org/blog/typology-people-people-diplomacy}{A
Typology of People-to-People Diplomacy}, USC Center on Public Diplomacy

2020,
\href{https://www.uscpublicdiplomacy.org/blog/measuring-country-images-four-lessons-south-korea?utm_source=hootsuite\&utm_medium=\&utm_term=\&utm_content=\&utm_campaign=}{Measuring
Country Images: Four Lessons from South Korea}, USC Center on Public
Diplomacy (Sevin, E., \textbf{Ayhan, K.} J.¸Ingenhoff, D.,)

2019,
\href{https://www.uscpublicdiplomacy.org/blog/let\%E2\%80\%99s-delineate-boundaries-public-diplomacy}{Let's
Delineate the Boundaries of Public Diplomacy}, USC Center on Public
Diplomacy

2018,
\href{https://www.uscpublicdiplomacy.org/blog/inter-korean-people-people-diplomacy}{Inter-Korean
People-to-People Diplomacy}, USC Center on Public Diplomacy

\textbf{Columns in English (selected)}

2019.08.15,
\href{http://www.koreaherald.com/view.php?ud=20190815000192}{S. Korea,
Japan should not let politics override personal ties},
\textbf{Ayhan, K.} J., Snow, N.

2018.11.03,
\href{http://www.koreatimes.co.kr/www/opinion/2018/11/734_258046.html}{Thinking
out loud about public diplomacy in Korea and beyond}, Snow N.,
\textbf{Ayhan, K.} J.

\textbf{Columns in Korean (selected)}

2020.02.07,
\href{https://www.donga.com/news/List/Series_70040100000265/article/all/20200207/99578393/1}{Korea
as Reflected on Twitter}

2019.09.20,
\href{http://www.donga.com/news/article/all/20190920/97489317/1}{21st
Century Diplomat should be on the Streets}

2019.07.12,
\href{https://www.donga.com/news/List/Series_70040100000265/article/all/20190712/96438479/1}{The
Importance of Inter-Korean Relations amid Talks of Co-hosting the World
Cup}

2019.06.07,
\href{https://www.donga.com/news/List/Series_70040100000265/article/all/20190607/95879632/1}{South
and North Korea as Seen from Washington}

2019.05.03,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20190503/95363228/1}{`We'
are the Strength of Korea}

2019.03.26,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20190326/94729975/1}{Why
Does a ``Multicultural'' Kid Has to go Gyeongbok Palace So Many Times?}

2018.12.04,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20181204/93139052/1}{For
MIKTA to Succeed}

2018.10.30,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20181030/92643028/1}{Before
Burning all the Bridges in International Relations}, \textbf{Ayhan, K.}
J., Snow, N.

2018.08.14,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20180814/91504198/1}{Just
about to Get Respect as a Middle Power}

2018.07.03,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20180703/90869259/1}{GKS
Students' Views on Korea}

2018.05.08,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20180508/89969581/1}{If
the Research Centers Have Freedom of Expression, Public Diplomacy
Blossoms}

2018.04.03,
\href{http://www.donga.com/news/List/Series_70040100000265/article/all/20180403/89427899/1}{What
is There to Fear in in Inter-Korean Exchanges?}

\hypertarget{languages}{%
\section{Languages}\label{languages}}

Turkish - Native

English - Fluent

Korean -- Fluent

\hypertarget{references}{%
\section{References}\label{references}}

Available upon request.



\end{document}
